Analysis of cycling potential around key corridors in Greater Manchester

### 2020-05-19 code/mcr-safe-streets-analysis.Rmd
Final tweaks to mcr analysis

---
title: "Analysis of cycling potential around key corridors in Greater Manchester"
author: "Robin Lovelace"
date: "18/05/2020"
# output: bookdown::html_document2
output: bookdown::word_document2
# output: bookdown::pdf_document2
---

```{r, echo=FALSE, eval=FALSE}

@@

Greater Manchester has high cycling potential and high reliance on public transport (PT) .
Across the region overall, 14.3% of commutes were made by public transport in 2011, although the reliance on public transport varies substantially across the region.
Around a third of trips are made by PT in many parts of Manchester and Salford, as shown in Figure \@ref(fig:pt).
These areas areas that are particularly vulnerable to reduced capacity by public transport also tend to be within cycling distance from the main employment centre in Manchester's city centre.

>>>>

---
title: "Analysis of cycling potential around key corridors in Greater Manchester"
author: "Robin Lovelace"
date: "18/05/2020"
# output: bookdown::html_document2
# output: bookdown::word_document2
output: bookdown::github_document2
# output: bookdown::pdf_document2
---

```{r, echo=FALSE, eval=FALSE}
pagedown::chrome_print("mcr-safe-streets-analysis.html")
```

@@

Greater Manchester has high cycling potential and high reliance on public transport (PT) .
Across the region overall, 14.3% of commutes were made by public transport in 2011, although the reliance on public transport varies substantially across the region.
Around a third of trips are made by PT in many parts of Manchester and Salford, as shown in Figure \@ref(fig:pt).
These areas that are particularly vulnerable to reduced capacity by public transport also tend to be within cycling distance from the main employment hub in Manchester's city centre.
